Hierarchical Dispatching and Overriding

### 2017-09-30 NewVersion/sections/Overview.tex
Section 2

\subsection{Problem 2: Dynamic Dispatch for Code Reuse}\label{subsec:problem2}

\bruno{Emphasizing hierarchical dispatch and triangle inheritance.}\haoyuan{Done}
On the other hand, we also need dynamic dispatch as it is essential and widely used in Object-Oriented programming.
C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, 
we redefine \lstinline|Deck| to support
both \lstinline|draw| and another operation called \lstinline|shuffleAndDraw|:
\vspace{3pt}\begin{lstlisting}
interface Deck {
  void draw() {...}
  void shuffleAndDraw() { shuffle(); draw(); }
  ...
}
\end{lstlisting}\vspace{3pt}
\lstinline|shuffleAndDraw| is a typical method that invokes \lstinline|draw| in its definition. In principle, we want
that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck| and override \lstinline|draw|:
\vspace{3pt}\begin{lstlisting}
interface LoggingDeck extends Deck {
  void draw() { // overriding
    Stack<Card> cards = this.getStack();
    if (!cards.isEmpty()) {
      Card card = cards.pop();
      println("The card is: " + card.toString());
      ...
    } else println("Empty deck.");
  }
}
\end{lstlisting}\vspace{3pt}
In that case, \lstinline|shuffleAndDraw| needs to be adapted to the new \lstinline|draw|. But due to static dispatch,
it still refers to the old \lstinline|draw| in \lstinline|Deck|. Thus programmers have to copy the \lstinline|shuffleAndDraw| code in
\lstinline|LoggingDeck|. It requires a lot of redundant work if we have to duplicate all such methods. Hence in order for code reuse,
we cannot just rely on static dispatch. However, as seen before, dynamic dispatch would take us back to problem 1, for instance, when we
have the UML in Figure~\ref{fig:drawableloggingdeck} and the following code:
\vspace{3pt}\begin{lstlisting}
interface DrawableLoggingDeck extends Drawable, LoggingDeck {...}
// main program
DrawableLoggingDeck d = new DrawableLoggingDeck();
d.shuffleAndDraw(); // ambiguous draw if dynamically dispatched
\end{lstlisting}\vspace{3pt}

>>>>

\subsection{Problem 2: Dynamic Dispatch for Code Reuse}\label{subsec:problem2}
Dynamic dispatching is essential and widely used in Object-Oriented programming.
C++ has the flexibility for choosing either way of dispatch by the \kwvirtual{} keyword.
Unfortunately, this approach is still unsatisfactory regarding code reuse. For instance, 
we redefine \lstinline|Deck| to support
both \lstinline|draw| and another operation called \lstinline|shuffleAndDraw|:
\vspace{3pt}\begin{lstlisting}
interface Deck {
  void draw() {...}
  void shuffleAndDraw() { shuffle(); draw(); }
  ...
}
\end{lstlisting}\vspace{3pt}
\lstinline|shuffleAndDraw| is a typical method that invokes \lstinline|draw| in its definition. In principle, we want
that invocation to use dynamic dispatch, because a programmer may define a subtype of \lstinline|Deck| and override \lstinline|draw|:
\vspace{3pt}\begin{lstlisting}
interface LoggingDeck extends Deck {
  void draw() { // overriding
    Stack<Card> cards = this.getStack();
    if (!cards.isEmpty()) {
      Card card = cards.pop();
      println("The card is: " + card.toString());
      ...
    } else println("Empty deck.");
  }
}
\end{lstlisting}\vspace{3pt}
In that case, \lstinline|shuffleAndDraw| needs to be adapted to the new \lstinline|draw|. But due to static dispatch,
it still refers to the old \lstinline|draw| in
\lstinline|Deck|\bruno{Is this discussion up-to-date? Please revise
  the discussion in view of what we know about C++ now.}. Thus programmers have to copy the \lstinline|shuffleAndDraw| code in
\lstinline|LoggingDeck|. It requires a lot of redundant work if we have to duplicate all such methods. Hence in order for code reuse,
we cannot just rely on static dispatch. However, as seen before, dynamic dispatch would take us back to problem 1, for instance, when we
have the UML in Figure~\ref{fig:drawableloggingdeck} and the following code:
\vspace{3pt}\begin{lstlisting}
interface DrawableLoggingDeck extends Drawable, LoggingDeck {...}
// main program
DrawableLoggingDeck d = new DrawableLoggingDeck();
d.shuffleAndDraw(); // ambiguous draw if dynamically dispatched
\end{lstlisting}\vspace{3pt}
